Mixed effect tweedie model in TMB

### 2020-03-09 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
plot new facet map of all temp estimates

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_revised")

@@

plot_map_raster(p_nd, "est") +
  scale_fill_viridis_c(trans = "log") +
  facet_wrap(~year) +
  ggtitle("Prediction (fixed effects + all random effects)")
```

>>>>

```{r}
p_nd <- readRDS("../VOCC/data/predicted_temp_allyears_revised")
# p_nd <- readRDS("~/github/dfo/gfranges/analysis/VOCC/data/predicted_temp_allyears_revised.rds")

@@

plot_map_raster(p_nd, "est") +
  scale_fill_viridis_c(trans = sqrt) +
  facet_wrap(~year) +
  ggtitle("Prediction (fixed effects + all random effects)")

test <- plot_facet_map(p_nd, "est", viridis_option = "D",
    raster_limits = c(min(p_nd$est),quantile(p_nd$est, 0.99)),
    transform_col = sqrt
  )
```
